\documentclass{resume}
\begin{document}

  \vfillForced

  \ResumeTitle{Lindsay William Bradford}
  
  \vfillForced
  
  \begin{ContactDetails}
    \ContactDetail{Availability}{February 2014}   
    \ContactDetail{Mobile Phone}{+61 423 989 511}   
    \ContactDetail{Email}{\href{mailto:lindsay.w.bradford@gmail.com}{lindsay.w.bradford@gmail.com}}   
  \end{ContactDetails}
  
  \vfillForced

  \begin{Profile}
  I am a highly motivated professional with excellent communication skills and a 
  wealth of software analysis, design and construction experience. I've coded back-end servers,
  rich GUI desktop applications for domains as diverse as stockbroking, rail control and 
  environmental modelling. 
  \end{Profile}

  \vfillForced

  \begin{Skills}
    \Skill{C\# / VB.NET}{Expert}{2--3}
    \Skill{Visual Studio}{Intermediate}{1.5}
    \Skill{ArcGIS, MapWinGIS}{Intermediate}{1.5}
    \Skill{Perl}{Intermediate}{> 1}
    \Skill{GIT}{Intermediate}{3}
    \Skill{Requirements Analysis}{Intermediate}{1.5--2}
    \Skill{Application/Architecture Analysis \& Design}{Expert}{> 5}
    \Skill{Unified Modelling Language (UML)}{Expert}{> 5}
    \Skill{Business Process Modelling (YAWL, EPC, BPMN)}{Advanced}{3}
    \Skill{Enterprise Architect}{Intermediate}{2}
    \Skill{Java}{Expert}{> 4}
    \Skill{Eclipse}{Advanced}{> 4}
    \Skill{XML}{Expert}{3--4}
    \Skill{SQL}{Advanced}{> 5}
    \Skill{Subversion (SVN)}{Advanced}{> 5}
  \end{Skills}

  \vfillForced

  \begin{Achievements}
   \Achievement{Proved via empirical analysis the viability of a prototype Web 
         Application Server capable of accepting and incorporating nearly 
         unrestricted software changes at runtime, and under extreme load. 
         This resulted in a published PhD thesis, three peer-reviewed articles, 
         two instances of national media coverage, and one patent.}
    \Achievement{Original author of the YAWLEditor, a workflow editor, allowing users 
          to quickly draw, validate and analyse YAWL workflow definitions. 
          Contributed to efforts showing that executable business processes could 
          be successfully applied to the highly creative domain of Film and Television.}
    \Achievement{Over a 7.5 year period, contributed in a number of increasingly 
          more senior roles to taking market share of the Shares Settlement 
          System from a handful of Brisbane Stockbrokers to over half of the 
          60-odd Australian Stockbroker community.}
  \end{Achievements}

  \pagebreakForcedFill

  \ResumeHeader{WORK HISTORY}
  \begin{WorkHistory}
    \CareerDetailItem{Senior Software Engineer (Contract)}{Australian Rivers Institute}{Sep 2010 -- Feb 2014}{
      \item Three contracts, with {\bfseries two extensions} in the first contract.
      \item Construction and Open-Source release of of integration tool for natural resource managements tools and datasets called \href{https://github.com/LindsayBradford/MWCIT}{MWCIT}. 
      \item {\bfseries} Species Benefit Wetland Optimisations via Simulated Annealing in {\bfseries VB.NET}
      \item {\bfseries Software architecture} analysis for \href{http://www.track.gov.au/sites/track.boab.info/files/uploads/TRaCK\_1.4\_IntegratingKnowledge\_AdaptiveManag\_web.pdf}{Management Strategy Evaluation} (MSE) platform. 
      \item {\bfseries VB.NET Programming:} multiple GUI \& infrastructure enhancements to MSE.
%      \item Prepared {\bfseries journal article} draft describing the architecture and design of the MSE.
      \item Usage of .NET ODBC, OLE and LINQ API libraries.
      \item Software {\bfseries profiling} and speed enhancements via \href{http://www.red-gate.com/products/dotnet-development/dotnet-developer-bundle/}{RedGate ANTS} suite.
      \item Usage of \href{http://www.esri.com/software/arcgis/}{ArcGIS}, \href{http://mapwingis.codeplex.com/}{MapWinGIS}, \href{http://www.syncfusion.com/}{Syncfusion}, \href{http://www.centerspace.net/products/c-sharp-vb-net-math-library-products/}{NMath}, and \href{http://www.r-project.org/}{R-language} tools.
%      \item Migration of web-content between ISPs. {\bfseries Web-page administration} including restricted access FTP and Web pages. 
    }
    \CareerDetailItem{R\&D Systems Engineer}{Invensys Rail}{Mar 2008 -- Jun 2010}{
      \item {\bfseries Software architecture} \& design for \href{http://www.ertms.com/2007v2/what\_levels.html}{ERTMS Level 2} 
            demonstrator and Singapore DTL \href{http://en.wikipedia.org/wiki/Centralized\_traffic\_control}{CTC Software}.
      \item {\bfseries Requirements analysis} and management for ERTMS Level 2 demonstrator software and Singapore DTL CTC software.
      \item {\bfseries Training preparation \& delivery} for their  
            \href{http://www.wrsa.com.au/DEPT/Marketing/common/datasheets.nsf/96dcdd1c8dd4d06d4a2567c4000fd98e/c1b8e39637ec308cca2570c10081065c?OpenDocument}{failover/communications framework}.
    }
    \CareerDetailItem{Senior Research Associate}{Queensland University of Technology}{Mar 2006 -- Mar 2008}{
      \item Collaborated with \href{http://cci.edu.au/}{CCi} researchers and industry partners to create accurate {\bfseries business 
            process models} of film and television production using Event Process Chains (EPCs).
      \item Enhanced the \href{http://sourceforge.net/projects/yawl/files/YAWL\%20Editor/}{YAWLEditor} to 
         better support users that must adapt business process models to {\bfseries executable workflow models}.
    }
    \CareerDetailItem{Guest Lecturer and Tutor}{Queensland University of Technology}{Oct 2003 -- June 2007}{
         \item Tutored an introductory {\bfseries XML Technologies} subject for undergraduate students, covering XML, XPath, DTDs, XMLSchema and XBRL.
         \item Tutored and marked assignments for the subjects {\it Information Modelling for Databases} ({\bfseries SQL} and Z Schema) 
               and {\it Information System Modelling (Z Schema)}. 
         \item Guest lectured students in {\it unanticipated software evolution} 
             using a distributed object middleware, {\bfseries software architecture} and scalability limitations of {\bfseries Java Servlets}.
    }
  \end{WorkHistory}
  \begin{WorkHistory}
    \CareerDetailItem{PhD Student}{Queensland University of Technology}{Aug 2002 -- Jun 2006}{
       \item Proved via empirical analysis, viability of a {\bfseries prototype Web Application Server}
             capable of incorporating {\bfseries unrestricted programming changes} at runtime under load.
       \item Primary author of several \hyperlink{Publications}{refereed and {\bfseries published papers}}, 
             the last of which was the basis of an 
             \href{http://v3.espacenet.com/textdes?DB=EPODOC\&IDX=EP1670212\&F=0\&QPN=EP1670212}{{\bfseries EU Patent}}. 
       \item Gained {\bfseries  national exposure} in the research section of The Australian newspaper, and an interview on ABC Radio National.
    }
    \CareerDetailItem{Research Assistant}{Queensland University of Technology}{Sep 2003 -- Feb 2006}{
      \item Acted as research assistant on the \href{http://www.yawlfoundation.org/}{YAWL} project.
      \item Primary author of an open-source {\bfseries workflow editor}
            (the \href{http://sourceforge.net/projects/yawl/files/YAWL\%20Editor/}{YAWLEditor}), 
            making extensive use of the \href{http://www.jgraph.com/}{JGraph} open-source Java graphing framework.
    }
    \CareerDetailItem{Requirements Analyst (Contract)}{Queensland University of Technology}{May 2005 -- June 2005}{
      \item Engaged in a contract with the QUT Creative Industries Precinct to 
            {\bfseries analyse business requirements} for an asset management system. 
      \item Resulting {\bfseries requirements specification} produced was well received by stakeholders.
    } 
    \CareerDetailItem{Research Programmer}{Information Designers}{Mar 2006 -- Jan 2007}{
      \item Constructed {\bfseries software deployment framework} and {\bfseries commercially compelling prototypes}, drawing on PhD techniques. 
%      \item Key prototype showed how a number of components specialised in different areas, such as new feeds or calendaring, could interact to 
%            deliver filtered RSS feeds to a calendar, or calendar information to RSS feeds.
      \item Used the \href{https://rome.dev.java.net/}{ROME framework} for RSS feed manipulation 
            and \href{http://ical4j.sourceforge.net/}{iCal4j framework} for iCalendar manipulation.
    }
    \CareerDetailItem{Systems Architecture Team Leader}{GBST Holdings}{Jan 2001 -- 20 May 02}{
      \item Managed \& mentored the team of architects, each specialised in a particular product.  
      \item Role involved ensuring that GBST's software products were adequately balancing strategic 
            future direction enhancements against existing work commitments.
      \item Estimated and subsequently won the business for a Hong Kong adaptation of Shares, sized at 80 person-weeks and 
            valued at approximately \$2 million.
      \item Introduced a {\bfseries UML} 1.3-based object-oriented analysis and design technique. Trained architects and 20+ designers in its usage.
    }
  \end{WorkHistory}
  \begin{WorkHistory}
    \CareerDetailItem{Systems Architect}{GBST Holdings}{Apr 1999 -- Jan 2001}{
      \item Ensured \href{http://www.gbst.com/products/broker-services/shares-australia.aspx}{Shares} was adequately {\bfseries balancing strategic direction against existing work}.  
      \item Product of expertise circa 2002 had $\approx$ 2.3 million lines of code in 16,000 programs, covering 470 database tables. 
      \item {\bfseries Introduced technical special interest groups} to 80+ programmers and 20+ designers including email groups, FAQs and how-to guides.
      \item {\bfseries Analysed requirements for, designed and tested} a risk management tool for vetting and automatically placing orders per stockbroker-defined 
            rules for online trading.
    }
    \CareerDetailItem{Trading Thematic Team Leader}{GBST Holdings}{Mar 1997 -- Apr 1999}{
      \item Ran a team of nine programmers, ensuring all trading-related support activities, 
      enhancements and projects were adequately resourced and managed. 
      \item Included {\bfseries software design} and {\bfseries quality assurance} of team member designs.
    }
    \CareerDetailItem{Software Designer}{GBST Holdings}{Dec 1996 -- Mar 1997}{
      \item Tasked with designing the GBST Billing System which tracked the Internet trading history 
      of stockbroker's clients using the GBST Online Internet trading portal. 
    }
    \CareerDetailItem{Application Support Team Leader}{GBST Holdings}{Oct 1996 - Dec 1996}{
      \item Ensured that team provided efficient, bug-free software and system data. Included ensuring real-time price, trade and security 
            feeds were being delivered and correctly applied to system. 
      \item Implemented a Support Blitz, {\bfseries taking 600 support requests to 200 in a fortnight}.
    }
    \CareerDetailItem{Software Designer/Team Leader}{GBST Holdings}{Dec 1995 -- Oct 1996}{
      \item {\bfseries Redesigned} End of Day (EOD) {\bfseries batch process into a phased solution}, allowing the 
            Shares System to remain online $24\times7\times365$. 
      \item Module reported only {\bfseries two bugs within first six months} of live operation.
      \item Acted as designer, programmer and tester on project, directing two other developers.
    }
    \CareerDetailItem{Application Support Team Member}{GBST Holdings}{Apr 1995 -- Dec 1995}{
      \item Acknowledged as the {\bfseries resident company expert} on portfolio (stock holdings).
      \item Built several support tools to alleviate manual portfolio support tasks.
    }
%    \CareerDetailItem{Research Assistant and Tutor}{University of Queensland}{Mar 1994 -- Feb 1995}{
%      \item {\bfseries Evaluated a distributed parallel algorithm package} for ANSI C by distributing NP-Complete calculations across university servers. 
%      \item Tutored subjects on {\it Structured Programming with Modula-2} and {\it Fundamentals of Operating Systems}.
%    }
  \end{WorkHistory}

  \pagebreakForcedFill

  \begin{EducationSummary}
    \EducationItem{2002--2006}{Doctor of Philosophy}{Queensland University of Technology}
    \EducationItem{1994}{Bachelor of Information Technology, Honours (2A)}{The University of Queensland}
    \EducationItem{1991--1993}{Bachelor of Information Technology}{The University of Queensland}
  \end{EducationSummary}  

  \vfillForced

  \begin{Publications}
    \Publication{Seidel, S., Rosemann, M., Ter Hofstede, A. H. M. and Bradford, L.:
                 Developing a business process reference model for the screen business -- a design science research case study.
                 The 17th Australasian Conference on Information Systems, Adelaide (2006).}
    \Publication{Bradford, L., Milliner, S., Dumas, M.:  
                 \href{http://www.springerlink.com/index/10.1007/11417019\_10}
                 {Experience using a Coordination-based Architecture for Adaptive Web Content Provision},
                 Proceedings of the 7th International Conference on Coordination Models and Languages, 
                 Springer-Verlag Heidelberg (2005). Acceptance ratio: 21.6\%.}
    \Publication{Bradford, L., Milliner, S., Dumas, M.:  
                 \href{http://www.springerlink.com/link.asp?id=qxg07vx8xyn71cw3}{Scaling Dynamic Web Content Provision Using Elapsed-Time-Based Content Degradation}, 
                 Proceedings of the 5th International Conference on Web Information Systems Engineering, Springer-Verlag Heidelberg (2004). Acceptance ratio: 22.7\%.}
    \Publication{Bradford, L., Milliner, S., Dumas, M.: 
                 \href{http://www.springerlink.com/link.asp?id=h38d8g1jlbtpufc4}{Varying Resource Consumption to Achieve Scalable Web Services}, 
                 Proceedings of the 4th VLDB Workshop on Technologies and E-Services, Springer-Verlag Heidelberg (2003).}
  \end{Publications}

  \vfillForced

  \begin{Patents}
    \Patent{Primary author of the EU patent 
       \href{http://v3.espacenet.com/textdes?DB=EPODOC\&IDX=EP1670212\&F=0\&QPN=EP1670212}{Adaptive software components}, 
        granted 17/10/2007.
    }
  \end{Patents}

  \vfillForced
  
  % Comment out the line below to remove the referees page from the Resume.

  %\input{referees}

\end{document}
